formula1

### 2020-07-22 inst/f1points.Rmd
tiny changes to filename

---
documentclass: jss
author:
  - name: Robin K. S. Hankin
    affiliation: Auckland University of Technology
    address: >
      2-14 Wakefield Street
      Auckland, New Zealand
    email: \email{hankin.robin@gmail.com}
    url: http://aut.ac.nz/
title:
  formatted: "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  plain:     "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  # For running headers, if needed
  short:     "Formula 1 Points Scoring"
abstract: >
  The point scoring system of Formula 1 motor racing is a long-standing
  contention among fans and competitors, with changes to the points
  scored occurring frequently.  Here, I apply generalized Plackett-Luce
  likelihood functions to Formula 1 racing, and assess historical points
  scoring systems objectively.  In a well-defined sense, the points
  scoring system of 1985 is the best of the historical ones.  I make
  similar observations about related competitive situations including
  the Eurovision Song contest and XXX.
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

@@

```{r,makeatable}
table(real_winner_ok=OO[1,]>0,top3_winner_ok=OO[3,]>0)
save(OO,file="~/f.Rd")
```

>>>>

---
documentclass: jss
author:
  - name: Robin K. S. Hankin
    affiliation: Auckland University of Technology
    address: >
      2-14 Wakefield Street
      Auckland, New Zealand
    email: \email{hankin.robin@gmail.com}
    url: http://aut.ac.nz/
title:
  formatted: "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  plain:     "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  # For running headers, if needed
  short:     "Formula 1 Points Scoring"
abstract: >
  The point scoring system of Formula 1 motor racing is a long-standing
  contention among fans and competitors, with changes to the points
  scored occurring frequently.  Here, I apply generalized Plackett-Luce
  likelihood functions to Formula 1 racing, and assess historical points
  scoring systems objectively.  In a well-defined sense, the points
  scoring system of 1985 is the best of the historical ones.  I make
  similar observations about related competitive situations including
  the Eurovision Song contest and XXX.
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: 
  \usepackage{amsmath}
output: rticles::jss_article
---

@@

```{r,makeatable}
table(real_winner_ok=OO[1,]>0,top3_winner_ok=OO[3,]>0)
save(OO,file="~/rstudio/hyper2/inst/cache_results_2017.Rd")
```
